With the development of social networks, the scale of network data is increasing. The massive network data contains unprecedented opportunities and challenges for service providers. For service providers, they can use the data mining of large amounts of network data to guide business development. For example, through social network mining research, high-performance friend recommendation can be performed; financial services  can evade the risk of overdue or even fraud in credit transactions  through effective mining tasks. At the same time, massive network-based data poses enormous challenges. On the one hand, data processing and analysis for huge amounts of network-based data are very costly in storage and calculation; on the other hand, the real-world network data is in the process of evolution,  restarting network mining tasks is very costly whenever new nodes or edges are modified. Therefore, how to extract effective network information in network mining is a very worthy research topic. In the research of massive data processing, the method used to extract important information from the data is called data dimensionality reduction. Inspired by data dimensionality reduction, network embedding algorithms have attracted much attention in research in recent years.

The research object of this paper is the most common attribute network in the real scene. That is to say, the nodes in the network have a lot of node features in addition to the network connection structure. For example, the user nodes in the social network contain rich attribute information: account number, age, interest,  etc., the use of node attributes will be more advantageous to the learning task of network data. At the same time, another characteristic of attribute network is the research content of this paper, namely the dynamic evolution of the network. In this paper, a new network embedding algorithm based on Laplacian Eigenmaps for the network structure is proposed , and similarity calculation is used to preserve the high-order proximity of the network structure, that is, to retain the local information in the network that is greater than the first-degree neighbor. Based on this algorithm, a corresponding incremental network embedding algorithm is proposed to deal with the dynamic network. A new algorithm is proposed for node attributes to perform representation learning. The node attributes are different from the sparsity of the network structure and a method suitable for gradient descent is proposed.  At the same time, a corresponding incremental attributes representation learning algorithm is proposed for dynamic networks.

In this paper, experimental results show that the network representation and incremental representation have ideal accuracy and good time efficiency in subsequent node classification and link prediction tasks.
